Job mobility and earnings growth: diffrerent markets, different outcomes.

### 2018-09-14 draft.Rmd
Update draft.Rmd

We offer two findings. First, quits and promotions have significantly different effects on earnings growth, depsite both commonly labeled as "voluntary". Internal promotions yield higher pay for workers in both countries. Quits have a minor effect, which are largely explained by changes in working hours. Second, the effect of promotions is larger in Germany than in the UK. This suggests the premium tied to promotion is greater in Germany. This high premium may act as an incentive to commit to the firm instead of the market, hence the lower rate of mobility among German workers. The minor effect of internal promotion

The decline of career ladders and the “death” of careers (Cappelli, 1999) has prompted some to embrace flexible and mobile markets (Arthur and Rousseau, 2001, Tolbert, 1996). In the narrative, increased mobility is inevitable but workers are able to gain through quits what was on offer through promotion. Some argue the precarity and instability experienced by turbulent labour markets is good for workers overall, since efficient and successful businesses will pass earnings on to workers in the form of gains, like higher earnings and better conditions (Brown et al., 2008). Turbulent and mobile markets give workers choice and movement occurs through mobility to “better jobs”. Less often, the authors discuss the effects of involuntary mobility or immobility with a given employer. The aim of this paper is to consider the central claim that voluntary mobility rewards workers. The article first considers the effect of movement overall, then contrasts the effect by considering inter- and intra-firm mobility, and lastly contrasts the UK against Germany; two institutional contexts with separate capitalisms.

>>>>

We offer two findings. First, quits and promotions have significantly different effects on earnings growth, depsite both commonly labeled as "voluntary" mobility types. Internal promotions yield higher pay for workers in both countries. Quits have a minor effect, which are largely explained by changes in working hours. Second, the effect of promotions is larger in Germany than in the UK. This suggests the premium tied to promotion is greater in Germany. This high premium may act as an incentive to commit to the firm instead of the market, hence the lower rate of mobility among German workers. The minor effect of internal promotions in the UK, means workers must be able to pursue several promotions before seeing a substantial change in pay.

The decline of career ladders and the “death” of careers (Cappelli, 1999) has prompted some to embrace flexible and mobile markets (Arthur and Rousseau, 2001, Tolbert, 1996). The narrative suggests that workers are able to gain through quits what was on offer through promotion. Our findings suggest that promotion and quits are distinctly different mechanisms for improving earnings. Further countries with limited mobility between firms, also have high rewards tied to internal mobility.

The article is structured as follows; section one summarises the theoretical literature on job mobility and earnings. Section two considers the theretical literature on country differences in labour market institutions. Section three outlines empirical findings and introduces our hypothesis. Section four summarises our methodology. Section five lists the results, and a brief cdiscussion cloncudes the article.
